Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex

\section{Evaluation}

@@

Our second dataset we will evaluate on is \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509}. This dataset
contains $581012$ description of geographical area (elevation, inclination,
etc...) and the goal is to predict the type of forest growing there. We picked
this one for couple of reasons. First it is simple that we can reach good
accuracy with only a few layers. This important because we want to show that
\textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
are sampling the entire space of possible sizes. The second reason is that [ref]
also perform their evaluation on this dataset, which allow us to compare the
results obtained by the two methods.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary}
\vspace*{-5mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset}
\end{center}
\vspace*{-4mm}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{size_evolution}
\vspace*{-5mm} \caption{\label{network_size_evolution} Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy
} \end{center}
\vspace*{-4mm}
\end{figure}

>>>>

%!TEX root=paper.tex
\section{Evaluation}

@@

The second dataset we use for evaluation the \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset. This dataset
contains $581012$ description of geographical area (elevation, inclination,
etc...) and the goal is to predict the type of forest growing there. We picked
this dataset for several reasons. First it is simple, such that we can reach good
accuracy with only a few layers. This important because we want to show that
\textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
are sampling the entire space of possible network sizes. The second reason is that Scardapane et al~\cite{Scardapane2017}
also perform their evaluation on this dataset, which allow us to compare the
results obtained by the two methods. \srm{what two methods?}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary}
\vspace*{-5mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset
\srm{label the x axes on the bottom plots}
}
\end{center}
\vspace*{-4mm}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{size_evolution}
\vspace*{-5mm} \caption{\label{network_size_evolution} Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy. 
} \end{center}
\vspace*{-4mm}
\end{figure}
